\LARGE{{\bf{Gravitational Wave Signals from Multiple Hidden Sectors} \\ }}

### 2019-09-03 gwnnDraft02.tex
signal updated

\email{
PaulSmith3@cmail.carleton.ca \\
}

@@

A SFOPT proceeds through bubble nucleation, where bubbles of the hadron form in the vacuum of quark phase. These bubbles will expand, eventually colliding and merging until the entire sector is within the new phase.  These bubbles are described by the following Euclidean action~\cite{}
%
\begin{equation}
S_{E}(T) = \frac{1}{T}\int d^3x \bigg[\frac{1}{2}(\nabla\phi)^2 + V(\phi,T)  \bigg],
\end{equation}
\draftnote{What is $\phi$?} where the time component has been integrated out due to finite temperature effects. The system has solutions with a $O(3)$ symmetry. We leave the thermalized potential $V(\phi, T)$ general, since an exact QCD potential at the time of the chiral phase transition is not well understood. Some authors~\cite{} have used the chiral effective Lagrangian to calculate a low energy thermalized potential for confining $SU(N)$ .

The amount of energy density dumped into the individual sectors dictates the energy budget for the PT and hence for the gravitational waves.  A quantity that characterizes the strength of the PT is the ratio of the latent heat of the phase transition $\epsilon$ to the energy density of radiation, at the time of nucleation, 
\begin{equation}
\alpha = \frac{\epsilon}{g_{*} \pi^2 (T^{nuc}_{\gamma})^4/30},
\label{eq:alpha}
\end{equation}
with $\epsilon$ being calculable from the scalar potential. Assuming that there is a negligible amount of energy being dumped back into the SM, which would cause significant reheating of $\rho_{\gamma}$,  $\epsilon$ should approximately be equal to the energy density of the hidden sector going through the PT. \draftnote{What about the energy in photons, neutrinos, etc?}
The parameter $g_{*}$ in the denominator of Eq.~(\ref{eq:alpha}) \draftnote{define $g_*$}. It has weak temperature dependence in a single sector, but when dealing with multiple hidden sectors, $g_{*}$ gains contributions from all $N$ sector's relativistic degrees of freedom, weighted by their respective temperature ratios (energy densities).
\begin{equation}
g_{*} = g_{*,\gamma} + \sum_{i} g_{*,i} (\xi_{i})^4
\end{equation}
with $\xi$ being the temperature ratio defined in Eq.~(\ref{eq:xi}). The bounds from effective number of neutrinos mean that $\xi_i \lesssim 1$ for all $i$, so $g_{*} \approx g_{*,\gamma}$. In the case of dark QCD-like chiral  phase transitions, the temperature of the phase transition is on the the order of the symmetry breaking scale of the respective sector, $T_{h}^{i} \sim \mathcal{O}(\Lambda_{QCD,i})$. Some authors \cite{bai, etc} have looked at calculating $\alpha$ through the low energy effective chiral Lagrangian for $SU(6)_{L} \times SU(6)_{R}$ breaking. We take the optimistic scenario, 
%
\begin{equation}
\alpha \approx \xi^{4} \approx \bigg( \frac{\Lambda_{d}}{T_{\gamma}^{nuc}}\bigg)^4
\end{equation}
%
where $T_{\gamma}^{nuc}$ is the temperature of the SM photon bath at the time of the phase transition. Another important parameter to characterize the phase transition is its inverse timescale \draftnote{define $\beta$}
\begin{equation}
\frac{\beta}{H} = T^{nuc}_h \frac{dS_{E}(T)}{dt}\bigg|_{t = t_{nuc}}
\end{equation}

@@

Gravitational waves are produced with contributions from different components of the SFOPT's evolution.  The energy in gravitational waves can be parameterized by \draftnote{Define $\Omega$ here}
The three leading order contributions to the GW power spectrum are as follows:
\begin{itemize}
\item \textbf{Scalar field contributions $\Omega_{\phi}$}: Caused by collisions of the bubble walls, the solutions being completely dependent on the scalar field configuration. With efficiency factor $\kappa_{\phi} = 1 - \alpha_{\infty}/\alpha$. \draftnote{Define $\alpha_{\infty}$}
\item \textbf{Sound wave contributions $\Omega_{v}$}: Sound waves within the plasma after bubble collision will produce $\beta/H$ \draftnote{\st{Define $\beta$ somewhere}} enhanced gravitational waves. With efficiency factor $\kappa_{v} \propto \alpha_{\infty}/\alpha$.
\item \textbf{Magnetohydrodynamics contributions $\Omega_{B}$}: MTG shocks within the plasma, left over from the sound wave propagation, will produce gravitational waves. With efficiency factor $\kappa_{
turb} \approx 0.1 \kappa_{v} $.
\end{itemize}
The total gravitational wave power spectrum \draftnote{Is $\Omega$ really a power spectrum? Isn't just an energy density?} is a linear combination of the three contributions,
\begin{equation}
h^2\Omega_{GW} \approx h^2\Omega_{\phi} + h^2\Omega_{v} + h^2\Omega_{turb} 
\end{equation}
In essence, this is a linear combination of the individual spectral shapes weighted by their efficiency factors $\kappa$.

\draftnote{Properly stich these paragraphs in here.}
These become relevant in the calculation of gravitational wave signatures through the calculation of the critical phase transition strength, $\alpha_{\infty}$, with $\alpha_{\infty}$ denotes the dividing line between the runaway regime  $(\alpha >\alpha_{\infty})$ and the non-runaway regime $(\alpha <\alpha_{\infty})$. Explicitly \cite{Breitbach:2018ddu, Caprini:2015zlo, Espinosa:2010hh}, 
\begin{equation}\label{eqn:critPTstrength}
\alpha_{\infty} = \frac{(T^{nuc}_h)^2}{\rho_R}\left[\sum_{bosons} n_i\frac{\Delta m^2_i}{24} + \sum_{fermions} n_i\frac{\Delta m_i^2}{48}\right],
\end{equation} 
for particles with $n_i$ degrees of freedom that obtain mass through the phase transition.

It should also be noted that although free quarks cease to exist post phase transition in these exotic sectors their masses are so light that they do not contribute relevant amounts to $\alpha_{\infty}$.

Exotic sectors feature no baryons and, as such, produce runaway bubbles similar to the exotic sectors in standard $N$naturalness.

Ultimately, calculating the critical phase transition strength for each sector using Eq.~(\ref{eqn:critPTstrength}) indicates that every sector has a phase transition in the runaway regime. Thus, all exotic sectors have strong first order phase transitions that lead to runaway bubble walls.

As shown in section IV, the mass spectrum from the dark QCD chiral breaking sectors is such that the runaway bubble condition is satisfied ($\alpha >\alpha_{\infty}$). In this case, the efficiency factors for sound wave and MHD contributions tend to zero and the GWs produced are purely from bubble collisions, $h^2\Omega_{GW} \approx h^2\Omega_{\phi}$.  The form of the GW power spectrum at the time of nucleation is given as,

\begin{equation}
h^2\Omega_{GW}^* = 7.7\times 10^{-2} \bigg( \frac{\kappa_{\phi} \alpha}{1 + \alpha} \bigg)^2 \bigg( \frac{H}{\beta} \bigg)^2  S(f)
\end{equation}
Where we have assumed an optimistic bubble wall velocity of $v \sim c$ for runaway bubbles. $S(f)$ is the frequency spectrum, \draftnote{What is the difference between $S(f)$ and $\Omega(f)$?} and a parametric from has been found through numerical simulations~\cite{} of bubble wall collisions.
\begin{equation}
S(f) = \frac{3.8 \,(f/f_p)^{2.8}}{1 + 2.8\,(f/f_p)^{3.8}}
\end{equation}
The peak frequency, $f_{p}$ is a function of the temperature of the SM at the time of nucleation. Depending on the model, \draftnote{How does it depend on the model? What goes into the below equation?} the various hidden sectors can phase transition at different scales and therefore temperatures, cause a shift in the GW spectrum's peak frequency given by~\cite{},

@@

\draftnote{\st{Define $g_*$}} Where $g_*$  is calculated using Eq.(12) \draftnote{Use Latex tags for equation referencing!}, although, due to the lack of substantial reheating into the hidden sectors, the SM contribution is dominant. Now that the framework has been laid out for the creation of GW from a single SFOPT, we generalize to multiple sectors going under independent, coherent SFOPT. In the models presented in this paper, we consider a subset of N-hidden sectors that phase transition at a SM temperature of $T_{\gamma}^{i}$. As the GWs propagate in free space, the energy density and frequency spectrum, at the time of production $\Omega_{GW}^{*}(f)$, will redshift to today's value $\Omega_{GW}^{0}(f) = \mathcal{A}\, \Omega_{GW}^{*}((a_{0}/a) f) $. The Redshift factor, $\mathcal{A}$, is related to the ratio of scale factors at the time of production and observation, and only scales with the relativistic degrees of freedom. \draftnote{ $ \mathcal{A} = a_{0}/a$??} Assuming that the sectors are completely decoupled before and after their respective SFOPT, the total GW power spectrum that would be measured today is given by the coherent sum,

\begin{equation}
\Omega_{GW}^{0} =  \sum_{i}^{N} \mathcal{A}^{i}\, \Omega_{GW}^{i,*}((a_{0}/a)_{i} f) 
\end{equation}

It is safe to assume that a subset of parameters of the SFOPT do not differ between sectors within Nnatrualness or other decoupled hidden sector models. In the case of N-copies of dark QCD-like phase transitions, the relativistic degrees of freedom, phase transition rate,  the dark QCD scale, are all similar. This makes the redshifting factor, $\mathcal{A}^i$, independent of sector number. We can also see that the frequency dependence in the spectrum takes the form of $f/f_{p}$, this causes a cancellation of the redshifting factors in the ratios. As multiple sectors phase transition at different times, and therefore temperatures, the peaks will shift relative to each other, purely from the linear temperature dependence of the peak frequency $f_{p} \sim T_{\gamma}$.  This is seen in figures \ref{}, where the spectrum peaks are shifted causing a peak broadening of the convoluted spectrum. The broadening can be substantial if the hidden sectors transition between a large gap of time (temperature). Eventually, a temperature limit will be reached at which two (or multiple) peaks, if the amplitudes are comparable.

\begin{figure}[tb]
\centering
\includegraphics[scale=.3]{Nnatral.png} 
\caption{ All contributions are assumed to be purely from bubble collisions $\Omega_{\phi}$, with $\beta/H  = 10$.  The shaded curves are the power law noise curves calculated from expected sensitivity curves for space-based interferometers and pulsar timing arrays; Lisa ( blue), DECIGO (light blue), BBO (red), SKA 5-year (purple), SKA 10-year (orange), SKA 20-year (green)   }
\end{figure}

\begin{figure*}[tb]
\centering
\begin{minipage}[c]{\textwidth}
\includegraphics[width=.45\textwidth]{TwoFar.png} 
\hfill
\includegraphics[width=.45\textwidth]{TwoMed.png} 
\hfill
\includegraphics[width=.45\textwidth ]{highest.png}
\hfill
\includegraphics[width=.45\textwidth]{energydensity.png} 
\end{minipage}
\hfill
\caption{ Gravitational wave power spectrum for various models. The top row consists of two models with only two hidden sectors undergoing SFOPT at differing temperatures. The bottom right (left) are examples of exotic sectors, discussed in section V, with sectors reheated at $T \sim 0.25\,T_{SM}$ ($T \sim 0.17\,T_{SM}$ ). All contributions are assumed to be purely from bubble collisions $\Omega_{\phi}$, with $\beta/H  = 10$.  The shaded curves are the power law noise curves calculated from expected sensitivity curves for space-based interferometers and pulsar timing arrays; Lisa ( blue), DECIGO (light blue), BBO (red), SKA 5-year (purple), SKA 10-year (orange), SKA 20-year (green)   }
\label{fig:Haa}
\end{figure*}

@@

Put description of calculation of experimental curves here.

>>>>

\email{
PaulSmith3@cmail.carleton.ca \\
Dylan.linthorne@carleton.ca \\
}

@@

A SFOPT proceeds through bubble nucleation, where bubbles of the hadron form in the vacuum of quark phase. These bubbles will expand, eventually colliding and merging until the entire sector is within the new phase.  These bubbles are described by the following Euclidean action~\cite{}
%
\begin{equation}\label{eqn:EuclideanAction}
S_{E}(T) = \frac{1}{T}\int d^3x \bigg[\frac{1}{2}(\nabla\phi)^2 + V(\phi,T)  \bigg],
\end{equation}
where the time component has been integrated out due to finite temperature effects. The system has solutions with a $O(3)$ symmetry. $\phi$ is the symmetry breaking scalar feild with a non-zero vev. In the case of the chiral phase transition, the scalar field breaking the SU$(6)_{R}$ $ \times$ SU$(6)_{L}$ chiral symmetry is the effective dark quark condensate $\phi \sim \langle q\bar{q} \rangle$. We leave the thermalized potential $V(\phi, T)$ general, since an exact QCD potential at the time of the chiral phase transition is not well understood. Some authors~\cite{} have used the chiral effective Lagrangian to calculate a low energy thermalized potential for confining SU$(N)$ .

The amount of energy density dumped into the individual sectors dictates the energy budget for the PT and hence for the gravitational waves. Assuming that the SM is radiation dominated, A quantity that characterizes the strength of the PT is the ratio of the latent heat of the phase transition $\epsilon$ to the energy density of radiation, at the time of nucleation,
\begin{equation}
\alpha     \equiv  \frac{\epsilon}{g_{*} \pi^2 (T^{nuc}_{\gamma})^4/30},
\label{eq:alpha}
\end{equation}
with $\epsilon$ being calculable from the scalar potential. Assuming that there is a negligible amount of energy being dumped back into the SM, which would cause significant reheating of $\rho_{\gamma}$,  $\epsilon$ should approximately be equal to the energy density of the hidden sector going through the PT. \draftnote{What about the energy in photons, neutrinos, etc?}
The parameter $g_{*}$ in the denominator of Eq.~(\ref{eq:alpha}) is the number of relativistic degrees of freedom at the time of the phase transition, with contributions from species in both the visible and dark sectors. It has weak temperature dependence in a single sector, but when dealing with multiple hidden sectors, $g_{*}$ gains contributions from all $N$ sector's relativistic degrees of freedom, weighted by their respective temperature ratios (energy densities).
\begin{equation}\label{eqn:RelaDOF}
g_{*} = g_{*,\gamma} + \sum_{i} g_{*,i} (\xi_{i})^4
\end{equation}
with $\xi$ being the temperature ratio defined in Eq.~(\ref{eq:xi}). The bounds from effective number of neutrinos mean that $\xi_i \lesssim 1$ for all $i$, so $g_{*} \approx g_{*,\gamma}$. In the case of dark QCD-like chiral  phase transitions, the temperature of the phase transition is on the the order of the symmetry breaking scale of the respective sector, $T_{h}^{i} \sim \mathcal{O}(\Lambda_{QCD,i})$. Some authors \cite{bai, etc} have looked at calculating $\alpha$ through the low energy effective chiral Lagrangian for $\textrm{SU(6)}_{L} \times \textrm{SU(6)}_{R}$ breaking. We take the optimistic scenario, 
%
\begin{equation}
\alpha_i \approx \xi_i^{4} \approx \bigg( \frac{\Lambda_{QCD,i}}{T_{\gamma}^{nuc}}\bigg)^4
\end{equation}
%
where $T_{\gamma}^{nuc}$ is the temperature of the SM photon bath at the time of the phase transition. Another important parameter to characterize the phase transition is its inverse timescale, $\beta$. The inverse timescale can be calculated using the action in Eq.~(\ref{eqn:EuclideanAction}),

\begin{equation}
\beta  \equiv \frac{dS_{E}(T)}{dt}\bigg|_{t = t_{nuc}}
\end{equation}

The ratio of $\beta$ and the hubble constant, at the time of nucleation, $H$ controls the strength of the GW signal,

\begin{equation}
\frac{\beta}{H} = T^{nuc}_h \frac{dS_{E}(T)}{dT}\bigg|_{T = T^{nuc}}
\end{equation}

@@

Gravitational waves are produced with contributions from different components of the SFOPT's evolution.  The spectral energy density in gravitational waves can be parameterized by $\Omega_{\textrm{GW}} (f) \equiv \frac{1}{ \rho_{c}} \frac{\textrm{d} \rho_{\textrm{GW}}(f) }{\textrm{dlog}(f)}$, where $\rho_{c} = 3H^2/(8 \pi G)$ is the critical energy density to not over close the universe. The three leading order contributions to the GW power spectrum are as follows:
\begin{itemize}
\item \textbf{Scalar field contributions $\Omega_{\phi}$}: Caused by collisions of the bubble walls, the solutions being completely dependent on the scalar field configuration. With efficiency factor $\kappa_{\phi} = 1 - \alpha_{\infty}/\alpha$. 
\item \textbf{Sound wave contributions $\Omega_{v}$}: Sound waves within the plasma after bubble collision will produce $\beta/H$ enhanced gravitational waves. With efficiency factor $\kappa_{v} \propto \alpha_{\infty}/\alpha$.
\item \textbf{Magnetohydrodynamical contributions $\Omega_{B}$}: MTG shocks within the plasma, left over from the sound wave propagation, will produce gravitational waves. With efficiency factor $\kappa_{
turb} \approx 0.1 \kappa_{v} $.
\end{itemize}

Where $\alpha_{\infty}$ denotes the dividing line between the runaway regime  $(\alpha >\alpha_{\infty})$ and the non-runaway regime $(\alpha <\alpha_{\infty})$. Explicitly \cite{Breitbach:2018ddu, Caprini:2015zlo, Espinosa:2010hh}, 
\begin{equation}\label{eqn:critPTstrength}
\alpha_{\infty} = \frac{(T^{nuc}_h)^2}{\rho_R}\left[\sum_{bosons} n_i\frac{\Delta m^2_i}{24} + \sum_{fermions} n_i\frac{\Delta m_i^2}{48}\right],
\end{equation} 
for particles with $n_i$ degrees of freedom that obtain mass through the phase transition. 
Exotic sectors feature no baryons and, as such, produce runaway bubbles similar to the exotic sectors in standard $N$naturalness\footnote {It should also be noted that although free quarks cease to exist post phase transition in these exotic sectors their masses are so light that they do not contribute relevant amounts to $\alpha_{\infty}$.}.

The total gravitational wave signal is a linear combination of the three contributions,
\begin{equation}
h^2\Omega_{\textrm{GW}} \approx h^2\Omega_{\phi} + h^2\Omega_{v} + h^2\Omega_{turb} 
\end{equation}
In essence, this is a linear combination of the individual spectral shapes weighted by their efficiency factors $\kappa$.

Ultimately, calculating the critical phase transition strength for each sector using Eq.~(\ref{eqn:critPTstrength}) indicates that every sector has a phase transition in the runaway regime. Thus, all exotic sectors have strong first order phase transitions that lead to runaway bubble walls ($\alpha >\alpha_{\infty}$). In this case, the efficiency factors for sound wave and MHD contributions tend to zero and the GWs produced are purely from bubble collisions, $h^2\Omega_{\textrm{GW}} \approx h^2\Omega_{\phi}$.  The form of the GW power spectrum at the time of nucleation is given as,

\begin{equation}
h^2\Omega_{\textrm{GW}}^* = 7.7\times 10^{-2} \bigg( \frac{\kappa_{\phi} \alpha}{1 + \alpha} \bigg)^2 \bigg( \frac{H}{\beta} \bigg)^2  S(f)
\end{equation}
Where we have assumed an optimistic bubble wall velocity of $v \sim c$ for runaway bubbles. $S(f)$ is the spectral shape function for the signal and a parametric from has been found through numerical simulations~\cite{} of bubble wall collisions.
\begin{equation}\label{eqn::spectralshape}
S(f) = \frac{3.8 \,(f/f_p)^{2.8}}{1 + 2.8\,(f/f_p)^{3.8}}
\end{equation}
The peak frequency, $f_{p}$ is a function of the temperature of the SM at the time of nucleation.  The various hidden sectors can phase transition at different scales and therefore temperatures, causing a shift in the GW spectrum's peak frequency given by~\cite{},

@@

Where $g_*$  is calculated using Eq.~(\ref{eqn:RelaDOF}) , although, due to the lack of substantial reheating into the hidden sectors, the SM contribution is dominant. Now that the framework has been laid out for the creation of GW from a single SFOPT, we generalize to multiple sectors going under independent, coherent SFOPT. In the models presented in this paper, we consider a subset of N-hidden sectors that phase transition at a SM temperature of $T_{\gamma}^{i}$. As the GWs propagate in free space, the energy density and frequency spectrum, at the time of production $\Omega_{\textrm{GW}}^{*}(f)$, will redshift to today's value $\Omega_{\textrm{GW}}^{0}(f) = \mathcal{A}\, \Omega_{\textrm{GW}}^{*}((a_{0}/a) f) $. The Redshifting factor, $\mathcal{A}$, accounts for the redshifting of both $\rho_{\textrm{GW}} $ and $\rho_{c}$~\cite{},

\begin{equation}\label{eqn::redshifting}
\mathcal{A} \equiv \bigg( \frac{a}{a_{0}} \bigg)^4 \bigg( \frac{H}{H_{0}}\bigg)^2
\end{equation}
where $a$ ($a_{0}$)  and $H$ ($H_{0}$) are the scale factor and Hubble constant at the time of nucleation (observation), respectfully. Assuming that the sectors are completely decoupled before and after their respective SFOPT, the total GW signal that would be measured today is given by the coherent sum,
\begin{equation}
\Omega_{\textrm{GW}}^{0} =  \sum_{i}^{N} \mathcal{A}^{i}\, \Omega_{\textrm{GW}}^{i,*}((a_{0}/a)_{i} f) 
\end{equation}
It is safe to assume that a subset of parameters of the SFOPT do not differ between sectors within Nnatrualness or other decoupled hidden sector models. In the case of N-copies of dark QCD-like phase transitions, the relativistic degrees of freedom, phase transition rate,  the dark QCD scale, are all similar. This makes the redshifting factor, $\mathcal{A}^i$, independent of sector number.

\begin{figure}[h!]
\centering
\includegraphics[scale=.3]{Nnatral.png} 
\caption{ All contributions are assumed to be purely from bubble collisions $\Omega_{\phi}$, with $\beta/H  = 10$.  The shaded curves are the power law noise curves calculated from expected sensitivity curves for space-based interferometers and pulsar timing arrays; Lisa ( blue), DECIGO (light blue), BBO (red), SKA 5-year (purple), SKA 10-year (orange), SKA 20-year (green)   }
\label{fig::Nnatural}
\end{figure}
Applying this to the standard reheating scenario of Nnatrualness, introduced in [], we get GW signals as seen in figure (\ref{fig::Nnatural}). Plotted are the individual contributions to the signal from each phase transistioned sector, as well as the coherent sum of all sectors. Future GW interferometers and pulsar timing array sensitivity curves are shown in comparison to the signal. The sensitivity curves are interpreted as the region of possible detection if intersected with the GW signal, more detail in the construction of these curves is given in the following section. Notice that the total signal is dominated by the first sectors contribution. This is caused by the quartic temperature ratio suppression in Eq. (\ref{eq:alpha}) and the large temperature gaps between adjacent sectors. Such a suppression leads to standard Nnatrualness evading future detector thresholds by a few orders of magnitude in units of energy density. This is not the case if we neglect the standard reheaton scenario and consider the generalized reheating scenarios of section [ref].

Assuming all else equal, we use the temperature schemes from Eq. (\ref{eqn:energyDensityAllowed}) to produce the plots in figure (\ref{fig:Haa}). In all cases, the summed GW signal is detectable by one or more proposed interferometers. The frequency dependence in Eq. \ref{eqn::spectralshape} takes the form of $f/f_{p}$, this causes a cancellation between the redshifting factors. As multiple sectors phase transition at different times, and therefore temperatures, the peaks will shift relative to each other, purely from the linear temperature dependence of the peak frequency $f_{p} \sim T_{\gamma}$.  This is seen in figure (\ref{fig:Haa}), where the spectrum peaks are shifted causing a peak broadening of the convoluted spectrum. The broadening can be substantial if the hidden sectors transition between a large gap of time (temperature). Eventually, a temperature limit will be reached at which two (or multiple) peaks, if the amplitudes are comparable.

\begin{figure*}[tb]
\centering
\begin{minipage}[c]{\textwidth}
\includegraphics[width=.45\textwidth]{TwoFar.png} 
\hfill
\includegraphics[width=.45\textwidth]{TwoMed.png} 
\hfill
\includegraphics[width=.45\textwidth ]{highest.png}
\hfill
\includegraphics[width=.45\textwidth]{energydensity.png} 
\end{minipage}
\hfill
\caption{ Gravitational wave power spectrum for various models. The top row consists of two models with only two hidden sectors undergoing SFOPT at differing temperatures. The bottom right (left) are examples of exotic sectors, discussed in section V, with sectors reheated at $T \sim 0.25\,T_{SM}$ ($T \sim 0.17\,T_{SM}$ ). All contributions are assumed to be purely from bubble collisions $\Omega_{\phi}$, with $\beta/H  = 10$.  The shaded curves are the power law noise curves calculated from expected sensitivity curves for space-based interferometers and pulsar timing arrays; Lisa ( blue), DECIO (light blue), BBO (red), SKA 5-year (purple), SKA 10-year (orange), SKA 20-year (green)   }
\label{fig:Haa}
\end{figure*}

@@

A unpolarized stocastic gravitational wave background could be detectable if the the signal-to-noise ratio (SNR) is above some threshold value, $\rho > \rho_{th}$, dictated by the capabilities of future interferometers and pulsar timing arrarys (PTA). These interferometers/PTAs quote their experimental sensistivies in terms of spectral noise curves, $S_{\textrm{eff}}(f)$, which can be translated into units of energy density through $h^2 \Omega_{\textrm{eff}}(f) = \frac{2\pi^2}{3H^2}f^3 S_{\textrm{eff}}(f)$. The cross correlated SNR for a specefied experimental setup is~\cite{}
\begin{equation}\label{eqn::SNR}
\rho^2 = 2 T \int_{f_{\textrm{min}}}^{f_{\textrm{max}}}\textrm{d}f \bigg( \frac{h^2 \Omega_{\textrm{GW}}(f)}{h^2 \Omega_{\textrm{eff}}(f)} \bigg)^2,
\end{equation}
Where $T$ is the exposure time of the experiment. The integration covers the entire broadband range of frequencies $(f_{\textrm{min}}, f_{\textrm{max}})$.

GW signals produced from an early cosmological phase transition would be seen as a stocastic background. Assuming that the GW follows a power law background in frequency, it is commonplace to quote the power law integrated (PLI) sensistivity curves~\cite{}. the PSI curves are constructed using information from the power law form of the signal,
\begin{equation}
h^2 \Omega_{\textrm{GW}}(f) = h^2 \Omega_{\beta}  \bigg(\frac{f}{f_{\textrm{ref}}}\bigg)^{\beta}
\end{equation}
where $\beta$ is the spectral index of the power law, and $f_{\textrm{ref}}$ is an arbitrary reference frequency which has no effect on the PLI sensetivities.

The method of calculating the PLI curves involves plotting $h^2 \Omega_{\textrm{GW}}(f) $, using Eq.~(\ref{eqn:RelaDOF}), for various spectral indices $\beta \in (-8,-7,-6, ... , 6, 7, 8)$ and for some fixed threshold value of $\rho_{th}$. Each curve will lay tangent to the PSI curve, more formally,
\begin{equation}
h^2 \Omega_{\textrm{PLI}} = \max\limits_{\beta}\bigg[ h^2 \Omega_{\beta}\bigg(\frac{f}{f_{\textrm{ref}}}\bigg)^{\beta}  \bigg].
\end{equation}
